The most obvious dynamic programming state, such as: $DP(c, cnt_A, cnt_B, cnt_C)$ = max score, considering only columns $[1..c]$, and using exactly $cnt_A$ A's, $cnt_B$ B's, and $cnt_C$ C's, will not work because it requires an $O(N^4)$ solution. What can we drop from the state?

We can try the following improvement: $DP(c, cnt_A, cnt_B)$ = max number of C's we can use, considering only columns $[1..c]$, and using exactly $cnt_A$ A's and $cnt_B$ B's. For each possible pair ($cnt_A$, $cnt_B$), we know the remaining number of empty cells (= number of all empty cells - $cnt_A$ - $cnt_B$). We then put at most $DP(N, cnt_A, cnt_B)$ C's to the empty cells, and calculate the score. By iterating over all possible pairs ($cnt_A$, $cnt_B$), we get the max score.

This solution runs in $O(N^3)$, which still exceeds the time limit. How to improve further?

Notice that we don't have any restriction on where to put the C's. We can use this advantage to drop one more state. Now, define $DP(c, cnt_A)$ = max number of B's we can use, considering only columns $[1..c]$, and using exactly $cnt_A$ A's. For each possible $cnt_A$, we first maximize the number of B's = $DP(N, cnt_A)$. We know the number of remaining empty cells (= number of all empty cells - $cnt_A$ - $DP(N, cnt_A)$). Then, we greedily do the following:

\begin{itemize}
  \item WLOG, let us assume that $S_a < S_b$.
  \item Put as many C's as possible to the remaining empty cells.
  \item If we still have C's, and $S_c > S_a$, replace as many A's as possible with C's.
  \item If we still have C's, and $S_c > S_b$, replace as many B's as possible with B's.
  \item After the number of A's, B's, and C's are fixed, we calculate the score.
\end{itemize}

By iterating over all possible $cnt_A$, we can get the max score. This solution runs in $O(N^2)$.
